# Reproducible Research: Peer Assessment 1
The goal of this report is to analyze...

## Loading and preprocessing the data
Data is in ```activity.zip```, included in this repository. It must be unzipped and read in:

```{r}
unzip("activity.zip")
data <- read.csv("activity.csv")
data$date <- as.Date(data$date)
```

## What is mean total number of steps taken per day?
To determine the mean total number of steps taken per day, we can use the ```aggregate``` function to sum steps per date:
```{r}
by.date <- aggregate(steps ~ date, data=data, FUN = sum, na.rm=TRUE)
steps <- by.date$steps
hist(steps, main="Frequency of Daily Step Counts")
```

We use the the ```mean``` and ```median``` functions to find the mean and median steps taken in one day:
```{r}
mean(steps)
median(steps)
```

## What is the average daily activity pattern?

We once again use ```summaryBy``` to average the number of steps for each 5-minute interval across all days:
```{r}
by.interval <- summaryBy(steps ~ interval, data=data, FUN = mean, na.rm=TRUE)
names(by.interval) <- c("5-minute interval", "average steps")
plot(by.interval, type="l", main="Steps per 5-minute Interval averaged Across Days")
```

We use the ```max``` function to find the most busy daily interval:
```{r}
max(by.interval$"average steps")
```

## Imputing missing values

Of ```r nrow(data)``` observations in our data, we're missing ```r sum(is.na(data$steps))``` of them. To try to fill this out...


## Are there differences in activity patterns between weekdays and weekends?
